The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-02-25 response.txt

We thank the referee for the close reading of the paper and the insightful 
comments.  We provide a response to specific comments from the referee
and ths statistical editor below.

> There are some stylistic issues with the text. I have left comments inline
>  where appropriate.

> More generally, given the technical nature of the work being described here,
> I frequently found myself wanting a small code snippet that demonstrated the 
> new/improved functionality of the packages being described. Perhaps the 
> authors could find a way to include short code examples where appropriate, 
> either inline in the paper body or in the appendix.

We did include code snippets in the first astropy paper from 2013, and
it is not much work; we could use the same scripts to provide nicely
formatted code examples with appropriate syntax highlighting here. However,
we have made a conscious decision to avoid that this time as far as
possible. We will explain our reasoning below, but if the referee
insists, we can quickly add a few examples in a second revision.

The main reasons why we chose NOT to include code samples are:

- While we aim for stability, many of the newsest features are still
  considered provisional, meaning that their API can still change. The
  paper describes astropy 2.0, but at the time of writing this,
  astropy 3.0 is already released. We hope that this paper is useful
  for years to come. Code examples for a specific version are at risk
  of being outdated much sooner than that.

- Code examples belong in the documentation. In the documentation at
  cods.astropy.org we provide extensive examples with enough comments
  to actually understand what is going on. If readers are curious, we
  want them to read the documentation.

- It takes a lot of space to explain a code example well. Currently,
  the text lists the names of the most important classes or
  functions. To give a meaningful example that shows these classes in
  action and is useful to people not familiar with astropy (or even
  Python), we would have to detail several parameters and the format
  of the results. We think that it is more useful to explain the
  general concept in the paper and not the names and the specific
  implementation of the functions and parameters.

- Most new features would require some setup. For example, showing the
  code for WCS axis plotting is not very useful without loading an
  image with a WCS in it first. More complex features profit more from
  code examples, but they also require much more setup to make such an
  example self-consistent and useful. Again, the documentation is a better
  place for that.

### 2018-02-25 main.tex
additional fixes to mid-sections

The version numbering of the \astropypkg core package reflects this release
scheme: the core package version number uses the form \texttt{x.y.z}, where ``x'' is
advanced for LTS releases, ``y'' for non-LTS feature releases, and
``z'' for bugfix releases.

@@

As of \astropypkg version 2.0, units and quantities, prevalent in most of its
subpackages, have become a key concept for using the package as a whole.
Units are intimately entwined in the definition of astronomical coordinates;
thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
(see \sectionname~\ref{sec:coordinates}) depends on them.
For most other subpackages, quantities are at least accepted and often expected
by default.

@@

The \package{astropy.time} subpackage focuses on supporting time scales (e.g.,
UTC, TAI, UT1) and time formats (e.g., Julian date, modified Julian date) that
are commonly used in astronomy.
This functionality is needed, for example, to calculate barycentric corrections
or sidereal times.
\package{astropy.time} is currently built on the ERFA (\citealt{erfa}) C
library, which replicates the Standards of Fundamental Astronomy (SOFA;
\citealt{sofa}) but is licensed under a three-clause BSD license.
The package was described in detail in  \citet{astropy} and has
stayed stable for the last several versions of \astropypkg.
Thus, in what follows, we only highlight significant changes or new features
since the previous \astropy paper.

>>>>

The version numbering of the \astropypkg core package reflects this release
scheme: the core package version number uses the form \texttt{x.y.z}, where ``x'' is
advanced for LTS releases, ``y'' for non-LTS feature releases, and
``z'' for bugfix releases.  This is similar to 
Semantic Versioning\footnote{https://semver.org}.

@@

As of \astropypkg version 2.0, units and quantities, prevalent in most of its
subpackages, have become a key concept for using the package as a whole.
Units are intimately entwined in the definition of astronomical coordinates;
thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
(see \sectionname~\ref{sec:coordinates}) depends on them.
Most \astropypkg subpackages have been made compatible with \texttt{Quantity} 
objects, although they are not always required.

@@

The \package{astropy.time} subpackage focuses on supporting time scales (e.g.,
UTC, TAI, UT1) and time formats (e.g., Julian date, modified Julian date) that
are commonly used in astronomy.
This functionality is needed, for example, to calculate barycentric corrections
or sidereal times.
\package{astropy.time} is currently built on the ERFA (\citealt{erfa}) C
library, which replicates the Standards of Fundamental Astronomy (SOFA;
\citealt{sofa}) but is licensed under a three-clause BSD license.
The package was described in detail in  \citet{astropy} and has
remained stable for the last several versions of \astropypkg.
Thus, in what follows, we only highlight significant changes or new features
since the previous \astropy paper.
